msre core

### 2018-11-26 report/msrecore.tex
corrected wrong caption references

\begin{figure}[H]
  \centering
  \centering
  \fbox{\includegraphics[page=122,width=0.8\textwidth,trim={4cm 4.5cm 4cm 3cm},clip]{./references/ORNL-TM-3039.pdf}}
  \caption{reactor access nozzle showing 10- and 2-1/2 in. annuli  \parencite[figure 5.10]{ornl-tm-3229}.}
  \label{3039-fig5-10}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \centering
  \fbox{\includegraphics[page=123,width=0.8\textwidth,trim={4cm 8cm 2.5cm 3.5cm},clip]{./references/ORNL-TM-3039.pdf}}
  \caption{reactor fuel outlet strainer \parencite[figure 5.11]{ornl-tm-3229}.}
  \label{3039-fig5-11}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \centering
  \fbox{\includegraphics[page=130,width=0.8\textwidth,trim={3.8cm 3.7cm 3.5cm 2.5cm},clip,angle=0.25]{./references/ORNL-TM-3039.pdf}}
  \caption{msre surveillance facility inside reactor vessel \parencite[figure 5.14]{ornl-tm-3229}.}
  \label{3039-fig5-11}
\end{figure}

>>>>

\begin{figure}[H]
  \centering
  \centering
  \fbox{\includegraphics[page=122,width=0.8\textwidth,trim={4cm 4.5cm 4cm 3cm},clip]{./references/ORNL-TM-3039.pdf}}
  \caption{reactor access nozzle showing 10- and 2-1/2 in. annuli  \parencite[figure 5.10]{ornl-tm-3039}.}
  \label{3039-fig5-10}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \centering
  \fbox{\includegraphics[page=123,width=0.8\textwidth,trim={4cm 8cm 2.5cm 3.5cm},clip]{./references/ORNL-TM-3039.pdf}}
  \caption{reactor fuel outlet strainer \parencite[figure 5.11]{ornl-tm-3039}.}
  \label{3039-fig5-11}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \centering
  \fbox{\includegraphics[page=130,width=0.8\textwidth,trim={3.8cm 3.7cm 3.5cm 2.5cm},clip,angle=0.25]{./references/ORNL-TM-3039.pdf}}
  \caption{msre surveillance facility inside reactor vessel \parencite[figure 5.14]{ornl-tm-3039}.}
  \label{3039-fig5-11}
\end{figure}
